\documentclass{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{graphicx}

\hypersetup{
  colorlinks=true,       % false: boxed links; true: colored links
  linkcolor=red,          % color of internal links (change box color
  % with linkbordercolor)
  citecolor=green,        % color of links to bibliography
  filecolor=magenta,      % color of file links
  urlcolor=cyan           % color of external links
}

\title{Hazard Analysis\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle
\thispagestyle{empty}

~\newpage

\pagenumbering{roman}

\begin{table}[hp]
  \caption{Revision History} \label{TblRevisionHistory}
  \begin{tabularx}{\textwidth}{llX}
    \toprule
    \textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
    \midrule
    Date1 & Name(s) & Description of changes\\
    Date2 & Name(s) & Description of changes\\
    ... & ... & ...\\
    \bottomrule
  \end{tabularx}
\end{table}

~\newpage

\tableofcontents

~\newpage

\pagenumbering{arabic}

\wss{You are free to modify this template.}

\section{Introduction}

\wss{You can include your definition of what a hazard is here.}

Hazards can be defined as either a state of the system or an action
taken on the system, which causes system failures. System failures
include, but are not limited to, an inability of the system to
perform its required functions, loss of data, unauthorized access,
or harm to users.

\section{Scope and Purpose of Hazard Analysis}

\wss{You should say what \textbf{loss} could be incurred because of the
hazards.}

\section{System Boundaries and Components}

\wss{Dividing the system into components will help you brainstorm the hazards.
  You shouldn't do a full design of the components, just get a feel
  for the major
  ones.  For projects that involve hardware, the components will
  typically include
  each individual piece of hardware.  If your software will have a
  database, or an
important library, these are also potential components.}

\section{Critical Assumptions}

\wss{These assumptions that are made about the software or system.  You should
  minimize the number of assumptions that remove potential hazards.
  For instance,
  you could assume a part will never fail, but it is generally better to include
this potential failure mode.}

\section{Failure Mode and Effect Analysis}

\wss{Include your FMEA table here. This is the most important part of
this document.}
\wss{The safety requirements in the table do not have to have the prefix SR.
  The most important thing is to show traceability to your SRS. You
  might trace to
  requirements you have already written, or you might need to add new
requirements.}
\wss{If no safety requirement can be devised, other mitigation strategies can be
  entered in the table, including strategies involving providing additional
documentation, and/or test cases.}

\begin{table}
  \scalebox{0.6}{
    \begin{tabular}{|>{\raggedright}p{2.0cm}|>{\raggedright}p{2.0cm}|>{\raggedright}p{2.5cm}|>{\raggedright}p{4cm}|>{\raggedright}p{3cm}|>{\raggedright}p{4cm}|>{\raggedright}p{1.5cm}|p{1.5cm}|}
      \hline
      \textbf{Design Function} & \textbf{Failure Modes} & \textbf{Effects
      of Failure} & \textbf{Causes of Failure} & \textbf{Detection} &
      \textbf{Recommended Actions} & \textbf{SR} & \textbf{Ref.} \\
      \hline
      Geo-blocking & Geolocation is inaccurate & Contractor may be on
      site, but unable to follow entry/exit protocols & a. GPS
      Signal Blocked \newline b. Use of inaccurate Geolocation API
      \newline c. Out of date third-party databases \newline d.
      Device does not have a GPS \newline e. VPN usage & Error
      messages and logging & a. Report inaccurate location detection
      to manager & SR-AR1 & H1-1 \\
      \hline
      User Authentication & Unauthorized Access & Comprimises system
      security & a. Weak protocols for user authentication &
      Geo-blocking & a. Require multi-factor authentication \newline
      b. limit login attempts & SR-AR1 & H2-1 \\
      \cline{2-8}
      & User has higher access level than they should & User may be
      able to view or edit documents they should not be able to
      causing security concerns & a. Permission issue from database
      failure & detailed logs of all views and edits to documents
      from within the system & a. Allow administrator to adjust
      permissions & SR-AR2 \newline SR-AR3 \newline SR-IR1 & H2-2 \\
      \hline
      View Station Entry Protocols & Contractor Views Old Version of
      Entry Protocols & Contractor may view and abide by out-of-date
      and incorrect station entry protocols & a. Database Error &
      Send all documents that a contractor viewed to their manager
      for verification upon completion & a. Reupload newer version of
      entry protocol documents & SR-IR2 & H3-1 \\
      \cline{2-8}
      & Contractor Unable to Sign Documents & Contractor cannot start
      doing their work as they are unable to complete appropriate
      documentation & a. Permission issue from database failure &
      Error messages and logging & a. Allow administrator to adjust
      permissions & SR-AR1 \newline SR-AR4 & H3-2 \\
      \hline
    \end{tabular}
  }
  \caption{Failure Mode and Effect Analysis (FMEA) Table}
\end{table}

\section{Safety and Security Requirements}

\wss{Newly discovered requirements.  These should also be added to the SRS.  (A
rationale design process how and why to fake it.)}

\section{Roadmap}

\wss{Which safety requirements will be implemented as part of the
  capstone timeline?
Which requirements will be implemented in the future?}

\newpage{}

\section*{Appendix --- Reflection}

\wss{Not required for CAS 741}

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?
  \item What pain points did you experience during this deliverable, and how
    did you resolve them?
  \item Which of your listed risks had your team thought of before this
    deliverable, and which did you think of while doing this deliverable? For
    the latter ones (ones you thought of while doing the Hazard Analysis), how
    did they come about?
  \item Other than the risk of physical harm (some projects may not have any
    appreciable risks of this form), list at least 2 other types of risk in
    software products. Why are they important to consider?
\end{enumerate}

\end{document}
